---
title: "Multiple Linear Regression for Number of Cars per Household"
author: "Rainer Lempert"
date: '`r format(Sys.time())`'
output:
  bookdown::word_document2: null
  bookdown::pdf_document2:
    includes:
      before_body: template/doc_prefix.tex
      in_header: template/preamble.tex
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: no
    toc: no
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology.csl
bibliography: template/ref.bib
---

```{r, include=FALSE}
library(tidyverse)
library(chron) # for time manipulation
library(geosphere) # for counters!
library(broom) # for tidy()
library(knitr) # for kable()
library(data.table)
library(forcats)
library(xts)
library(TTR)
library(lubridate)
library(scales) 
library(gridExtra)
library(RColorBrewer)
library(stringr)
library(ggmap)
```

```{r, include=FALSE}
survey_data <- read_csv(file="DataSets/Vancity_CarSharing_Data.csv")
survey_data_2 <- read_csv(file="DataSets/Vancity_CarSharing_Data_Indices.csv")
```
# Develop The Model

33 dependent variables from the survey were chosen:

- Q6 - How long have you been a member of a CSO
- Reasons for CS use
	- Q7_1 - To reduce carbon footprint 
	- Q7_2 - To save money
	- Q7_3 - For convenience
	- Q7_4 - ‘Just in case’ you need it
	- Q7_5 - Because there is no Uber/Lyft in town
	- Q7_6 - Personal safety - safer than public transit
- Q8 - Have you disposed a vehicle and used CS instead
- Q9 - Without CS would you have bought or acquired a vehicle?
- Cost-related reasons for CS use
	- Q10_1 - CS saves me money because I don’t have to own a vehicle (or another vehicle)
	- Q10_2 - CS saves me money because it’s cheaper than using a taxi
	- Q10_3 - I look at the cost of CS vs cost of walking or biking
	- Q10_4 - I look at the cost of CS vs the cost of public transit
	- Q10_5 - I rarely evaluate the cost of using CS versus the alternatives
- Q11 - Can I afford another vehicle?
- Material benefits of CS
	- Q13_1 - Easier to meet up with friends and family
	- Q13_2 - I go to more places in the city
	- Q13_3 - I go to more places outside the city
	- Q13_4 - I get ‘stuff’ done more efficiently; errands, meetings, shopping, etc
- Mental benefits of CS
	- Q14_1 - I enjoy the freedom
	- Q14_2 - I like not having to rely on others for a ride
	- Q14_3 - Peace of mind knowing I have personal mobility when needed
	- Q14_4 - I like not owning a vehicle (or another vehicle)
	- Q14_5 - I like having different options for getting around
- Q15 - Has your CS use fallen off?
- Q23 - Age
- Q24 - Gender
- Q26 - Number of drivers per household
- Q27 - Number of vehicles per household
- Q28 - Number of children per household
- Q29 - Are you a homeowner
- Q30 - Affordability index
- Q31 - Income

Variables were chosen to be either numerical, ordinal, or binary. 
```{r, include=FALSE}
mydata<-survey_data_2 %>%
  mutate(type_of_cs=ifelse(is.na(Q4_1)&is.na(Q4_2)&is.na(Q4_3)&is.na(Q4_4),"None",
                    ifelse(!is.na(Q4_1)&is.na(Q4_2)&is.na(Q4_3)&is.na(Q4_4),"Two-Way",
                    ifelse(is.na(Q4_1)&!is.na(Q4_2)&is.na(Q4_3)&is.na(Q4_4),"Two-Way",
                    ifelse(is.na(Q4_1)&is.na(Q4_2)&!is.na(Q4_3)&is.na(Q4_4),"One-Way",
                    ifelse(is.na(Q4_1)&is.na(Q4_2)&is.na(Q4_3)&!is.na(Q4_4),"One-Way",
                    ifelse(!is.na(Q4_1)&!is.na(Q4_2)&is.na(Q4_3)&is.na(Q4_4),"Two-Way",
                    ifelse(!is.na(Q4_1)&is.na(Q4_2)&!is.na(Q4_3)&is.na(Q4_4),"Both",
                    ifelse(!is.na(Q4_1)&is.na(Q4_2)&is.na(Q4_3)&!is.na(Q4_4),"Both",
                    ifelse(is.na(Q4_1)&!is.na(Q4_2)&!is.na(Q4_3)&is.na(Q4_4),"Both",
                    ifelse(is.na(Q4_1)&!is.na(Q4_2)&is.na(Q4_3)&!is.na(Q4_4),"Both",
                    ifelse(is.na(Q4_1)&is.na(Q4_2)&!is.na(Q4_3)&!is.na(Q4_4),"One-Way",
                    ifelse(!is.na(Q4_1)&!is.na(Q4_2)&!is.na(Q4_3)&is.na(Q4_4),"Both", 
                    ifelse(!is.na(Q4_1)&!is.na(Q4_2)&is.na(Q4_3)&!is.na(Q4_4),"Both",
                    ifelse(!is.na(Q4_1)&is.na(Q4_2)&!is.na(Q4_3)&!is.na(Q4_4),"Both", 
                    ifelse(is.na(Q4_1)&!is.na(Q4_2)&!is.na(Q4_3)&!is.na(Q4_4),"Both", "Both")))))))))))))))) %>% 
	filter(
					!is.na(Q6)& #How long have you been a member?

				 	#Reasons for CS use
				 	!is.na(Q7_1)& #To reduce your carbon footprint and help the environment
				 	!is.na(Q7_2)& #To save money
				 	!is.na(Q7_3)& #For convenience
				 	!is.na(Q7_4)& #Your membership is 'just in case' you need it
				 	!is.na(Q7_5)& #Because we have no Uber/Lyft in town
				 	!is.na(Q7_6)& #Personal safety - safer than using public transit

				 	!is.na(Q8)& #Have you disposed a vehicle and used CS instead?
				 	!is.na(Q9)& #Without CS would you have bought or acquired a vehicle?

				 	#Cost-related reasons for CS use
				 	!is.na(Q10_1)& #CS saves me money because I don't have to own a vehicle (or another vehicle)
				 	!is.na(Q10_2)& #CS saves me money because it's cheaper than using a taxi
				 	!is.na(Q10_3)& #I look at the cost of CS vs cost of walking or biking
				 	!is.na(Q10_4)& #I look at the cost of CS vs the cost of public transit
				 	!is.na(Q10_5)& #I rarely evaluate the cost of using CS versus the alternatives

				 	!is.na(Q11)& #Can I afford another vehicle?

				 	#Material benefits of CS
				 	!is.na(Q13_1)& #Easier to meet up with friends and family
				 	!is.na(Q13_2)& #I go to more places in the city
				 	!is.na(Q13_3)& #I go to more places outside the city
				 	!is.na(Q13_4)& #I get 'stuff' done more efficiently; errands, meetings, shopping, etc

				 	#Mental benefits of CS
				 	!is.na(Q14_1)& #I enjoy the freedom
				 	!is.na(Q14_2)& #I like not having to rely on others for a ride
				 	!is.na(Q14_3)& #Peace of mind knowing I have personal mobility when needed
				 	!is.na(Q14_4)& #I like not owning a vehicle (or another vehicle)
				 	!is.na(Q14_5)& #I like having different options for getting around

				 	!is.na(Q15)& #Has your CS use fallen off?
				 	!is.na(Q23)& #Age
				 	!is.na(Q24)& #Gender
				 	!is.na(Q26_1_TEXT)& #Number of drivers per household
				 	!is.na(Q27_1_TEXT)& #Number of vehicles per household
				 	!is.na(Q28)& #Number of children per household
				 	!is.na(Q29)& #Are you a homeowner?
				 	!is.na(Q30)& #Affordability index
				 	!is.na(Q31)) #Income
```


```{r, include=FALSE}

mymodel <- lm(Q27_1_TEXT ~ Q6+
											Q7_1+
											Q7_2+
											Q7_3+
											Q7_4+
											Q7_5+
											Q7_6+
											Q8+
											Q9+
											Q10_1+
											Q10_2+
											Q10_3+
											Q10_4+
											Q10_5+
											Q11+
											Q13_1+
											Q13_2+
											Q13_3+
											Q13_4+
											Q14_1+
											Q14_2+
											Q14_3+
											Q14_4+
											Q14_5+
											Q15+
											Q23+
											Q24+
											Q26_1_TEXT+ 
										#	Q27+ 
											Q28+
											Q29+
											Q30+
											Q31, 
										data=mydata)
summary(mymodel)

```



# Results
```{r, echo=FALSE}
out <- tidy(mymodel)
out<-out %>%
	mutate(Sig.=if_else(p.value<0.001,"***",if_else(p.value<.01,"**",if_else(p.value<0.05,"*",if_else(p.value<0.1,"."," ")))))
kable(out)
```

After doing this analysis, these are the variables that have explanatory power (at an $\alpha = 0.05$) over type of CS usage:


- Q6 - How long have you been a member of a CSO
	- Correlation between people being members for longer periods of time and having fewer cars
- Q7_2 - To save money
	- Correlation between people agreeing and having more cars
- Q7_4 - ‘Just in case’ you need it
	- *STRONG* correlation between people agreeing and having more cars
- Q7_6 - Personal safety - safer than public transit
	- *STRONG* correlation between people agreeing and having more cars
- Q9 - Without CS would you have bought or acquired a vehicle?
	- 2=no, 1=yes.
	- Correlation between people agreeing and having more cars
- Q10_1 - CS saves me money because I don’t have to own a vehicle (or another vehicle)
	- Correlation between people agreeing and having fewer cars
- Q10_5 - I rarely evaluate the cost of using CS versus the alternatives
	- Correlation between people agreeing and having more cars
- Q11 - Can I afford another vehicle?
	- 2=no, 1=yes.
	- Correlation between people agreeing and having more cars (woo hoo)
- Q13_3 - I go to more places outside the city
	- *STRONG* correlation between people agreeing and having fewer cars
- Q13_4 - I get ‘stuff’ done more efficiently; errands, meetings, shopping, etc
	- *STRONG* correlation between people agreeing and having fewer cars
- Q14_4 - I like not owning a vehicle (or another vehicle)
	- *STRONG* correlation between people agreeing and haing fewer cars
- Q23 - Age
	- Correlation between people being older and using two-way over both
- Q24 - Gender
	- 2=female, 1=male.
	- Correlation between people being male and having more cars
- Q26 - Number of drivers per household
	- *STRONG* correlation between there more drivers per household and having more cars (woo hoo)
- Q29 - Are you a homeowner
	- 2=no, 1=yes
	- *STRONG* correlation between being a homeowner and having more cars
- Q30 - Affordability index
	- Correlation between finding Vancouver more affordable and having more cars











