---
title: "Untitled"
author: "Rainer"
date: "11/1/2017"
output: html_document
---

```{r}
library(tidyverse)
library(chron) # for time manipulation
library(geosphere) # for counters!
library(knitr)
library(data.table)
library(forcats)
library(xts)
library(TTR)
library(lubridate)
library(scales) 
library(gridExtra)
library(RColorBrewer)
library(stringr)
library(ggmap)
```

```{r}
survey_data <- read_csv(file="DataSets/Vancity_CarSharing_Data.csv")
survey_data_2 <- read_csv(file="DataSets/Vancity_CarSharing_Data_Indices.csv")
```





Clean the data set
```{r}
survey_data$StartDate<-as.Date(survey_data$StartDate, format="%m/%d/%y")
survey_data$EndDate<-as.Date(survey_data$EndDate, format="%m/%d/%y")
survey_data$Duration__in_seconds_<-as.double(survey_data$Duration__in_seconds_)

#https://stackoverflow.com/questions/20637360/convert-all-data-frame-character-columns-to-factors
survey_data <- as.data.frame(unclass(survey_data))
```

filter to make file for Matlab
```{r}
survey_data_2_export<-survey_data_2 %>% 
	filter(!is.na(Q3_1)&!is.na(Q3_2)&!is.na(Q3_3)&!is.na(Q3_4)&!is.na(Q3_5)&!is.na(Q3_6)&!is.na(Q3_7)&!is.na(Q3_8)&!is.na(Q6)) %>% 
	select(Q3_1,Q3_2,Q3_3,Q3_4,Q3_5,Q3_6,Q3_7,Q3_8)
```

export for matlab PCA
```{r}
write_csv(survey_data_2_export,"ride_utilization.csv")
```

after matlabings, (and manually renaming column headers) import file with PC values
```{r}
ride_utilization_PCs<-read_csv("ride_utilization_PCs.csv")
```

relevel for graphsfactors
```{r}
pca_analysis$Q3_1<-fct_relevel(pca_analysis$Q3_1,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
pca_analysis$Q3_2<-fct_relevel(pca_analysis$Q3_2,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
pca_analysis$Q3_3<-fct_relevel(pca_analysis$Q3_3,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
pca_analysis$Q3_4<-fct_relevel(pca_analysis$Q3_4,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
pca_analysis$Q3_5<-fct_relevel(pca_analysis$Q3_5,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
pca_analysis$Q3_6<-fct_relevel(pca_analysis$Q3_6,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
pca_analysis$Q3_7<-fct_relevel(pca_analysis$Q3_7,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
pca_analysis$Q3_8<-fct_relevel(pca_analysis$Q3_8,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
```

first look at the first 2 PCs. Hopefully patterns will emerge... I guess we'll see.
```{r}
ride_utilization_PCs %>% 
	ggplot(aes(x=PC1,y=PC2))+
	geom_point()
```
prepping our survey data for analysis
```{r}
survey_data<-survey_data %>% 
	filter(!is.na(Q3_1)&!is.na(Q3_2)&!is.na(Q3_3)&!is.na(Q3_4)&!is.na(Q3_5)&!is.na(Q3_6)&!is.na(Q3_7)&!is.na(Q3_8)&!is.na(Q6))
```

creating pca analysis data frame
```{r}
pca_analysis<-cbind(survey_data,ride_utilization_PCs)
```

```{r}
pca_analysis<-pca_analysis %>%
  mutate(Carshare_Type=ifelse(is.na(Q4_1)&is.na(Q4_2)&is.na(Q4_3)&is.na(Q4_4),"None",
                    ifelse(!is.na(Q4_1)&is.na(Q4_2)&is.na(Q4_3)&is.na(Q4_4),"Only Two-way",
                    ifelse(is.na(Q4_1)&!is.na(Q4_2)&is.na(Q4_3)&is.na(Q4_4),"Only Two-way",
                    ifelse(is.na(Q4_1)&is.na(Q4_2)&!is.na(Q4_3)&is.na(Q4_4),"Only Free-floating",
                    ifelse(is.na(Q4_1)&is.na(Q4_2)&is.na(Q4_3)&!is.na(Q4_4),"Only Free-floating",
                    ifelse(!is.na(Q4_1)&!is.na(Q4_2)&is.na(Q4_3)&is.na(Q4_4),"Two-way & Free-floating",
                    ifelse(!is.na(Q4_1)&is.na(Q4_2)&!is.na(Q4_3)&is.na(Q4_4),"Only Two-way",
                    ifelse(!is.na(Q4_1)&is.na(Q4_2)&is.na(Q4_3)&!is.na(Q4_4),"Two-way & Free-floating",
                    ifelse(is.na(Q4_1)&!is.na(Q4_2)&!is.na(Q4_3)&is.na(Q4_4),"Two-way & Free-floating",
                    ifelse(is.na(Q4_1)&!is.na(Q4_2)&is.na(Q4_3)&!is.na(Q4_4),"Two-way & Free-floating",
                    ifelse(is.na(Q4_1)&is.na(Q4_2)&!is.na(Q4_3)&!is.na(Q4_4),"Only Free-floating",
                    ifelse(!is.na(Q4_1)&!is.na(Q4_2)&!is.na(Q4_3)&is.na(Q4_4),"Two-way & Free-floating", 
                    ifelse(!is.na(Q4_1)&!is.na(Q4_2)&is.na(Q4_3)&!is.na(Q4_4),"Two-way & Free-floating",
                    ifelse(!is.na(Q4_1)&is.na(Q4_2)&!is.na(Q4_3)&!is.na(Q4_4),"Two-way & Free-floating", 
                    ifelse(is.na(Q4_1)&!is.na(Q4_2)&!is.na(Q4_3)&!is.na(Q4_4),"Two-way & Free-floating", "Two-way & Free-floating"))))))))))))))))

pca_analysis$Carshare_Type<-as.factor(pca_analysis$Carshare_Type)

```

```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q3_1))+
	geom_point(alpha=0.7)+
	ggtitle("Walking")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q3_2))+
	geom_point(alpha=0.7)+
	ggtitle("Biking")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q3_3))+
	geom_point(alpha=0.7)+
	ggtitle("Public Transit")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q3_4))+
	geom_point(alpha=0.7)+
	ggtitle("Carpool/Vanpool")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q3_5))+
	geom_point(alpha=0.7)+
	ggtitle("Taxi")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q3_6))+
	geom_point(alpha=0.7)+
	ggtitle("Carshare")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q3_7))+
	geom_point(alpha=0.7)+
	ggtitle("Passenger in private car")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q3_8))+
	geom_point(alpha=0.7)+
	ggtitle("Driver in a private car")+
  theme(plot.title = element_text(hjust = 0.5))
```

Q9 shows something
```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q9))+
	geom_point(alpha=0.7)
```

Q11 as well
```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q11))+
	geom_point(alpha=0.7)
```

```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q23))+
	geom_point(alpha=0.7)
```

```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q25))+
	geom_point(alpha=0.7)
```

```{r}
pca_analysis %>% 
	ggplot(aes(x=PC1,y=PC2, color=Q29))+
	geom_point(alpha=0.7)
```


```{r}
pca_analysis %>%  
  filter(!is.na(Q18)) %>% 
  filter(!is.na(Carshare_Type)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Carshare_Type,Q18) %>%
  tally %>% 
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Carshare_Type,fill=Q18))+
  geom_bar(aes(weight=percent),position="stack")+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.title=element_blank())+
  ggtitle("Willingness to share vs carsharing service") +
  labs(x="What type of carsharing service(s) do you belong to",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  geom_text(aes(y = percent, label = paste(round(percent,digits=1),"%",sep="")), position = position_stack(vjust = 0.5), size=3)+
  coord_flip()
```

















```{r}
survey_data %>%
  group_by(Carshare_Type) %>% 
  tally %>% 
  ggplot(aes(x=Carshare_Type, y=n))+ 
  geom_histogram(stat="identity")
```

```{r}
survey_data %>%   
  filter(!is.na(Carshare_Type)) %>% 
  group_by(Carshare_Type,Q3_5) %>% 
  summarize(count=n()) %>% 
  complete(Q3_5, fill = list(count = 0)) %>% 
  mutate(percentage=count/sum(count)) 
```
```{r}
survey_data %>%   
  filter(!is.na(Carshare_Type)) %>% 
  group_by(Carshare_Type,Q3_5) %>% 
  summarize(count=n()) %>% 
  complete(Q3_5, fill = list(count = 0))

levels(survey_data$Q3_5)
```


```{r}
survey_data<-survey_data %>% 
  filter(Q3_5 %in% c("Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")) %>% 
  droplevels()
survey_data$Q3_5<-fct_expand(survey_data$Q3_5,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
survey_data$Q3_5<-fct_relevel(survey_data$Q3_5,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
levels(survey_data$Q3_5)
```


## Travel usage by type of CS


```{r}
v<-c(0,0.5,1.4,3.5,6,11,18)

survey_data<-survey_data %>% 
  filter(Carshare_Type!="None") %>% 
  droplevels()

survey_data<-survey_data %>% 
  filter(Q3_1 %in% c("Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips"))%>% 
  droplevels()

survey_data$Q3_1<-fct_expand(survey_data$Q3_1,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
survey_data$Q3_1<-fct_relevel(survey_data$Q3_1,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")

survey_data<-survey_data %>% 
  filter(Q3_2 %in% c("Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips"))%>% 
  droplevels()
survey_data$Q3_2<-fct_expand(survey_data$Q3_2,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
survey_data$Q3_2<-fct_relevel(survey_data$Q3_2,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")

survey_data<-survey_data %>% 
  filter(Q3_3 %in% c("Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips"))%>% 
  droplevels()
survey_data$Q3_3<-fct_expand(survey_data$Q3_3,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
survey_data$Q3_3<-fct_relevel(survey_data$Q3_3,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")

survey_data<-survey_data %>% 
  filter(Q3_4 %in% c("Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips"))%>% 
  droplevels()
survey_data$Q3_4<-fct_expand(survey_data$Q3_4,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
survey_data$Q3_4<-fct_relevel(survey_data$Q3_4,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")

survey_data<-survey_data %>% 
  filter(Q3_5 %in% c("Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")) %>% 
  droplevels()
survey_data$Q3_5<-fct_expand(survey_data$Q3_5,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
survey_data$Q3_5<-fct_relevel(survey_data$Q3_5,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")


e<-survey_data %>%   
  filter(!is.na(Carshare_Type)) %>% 
  group_by(Carshare_Type,Q3_5) %>% 
  summarize(count=n()) %>% 
  complete(Q3_5, fill = list(count = 0)) %>% 
  mutate(percentage=count/sum(count)) %>% 
  mutate(v) %>% 
  mutate(estimate=percentage*v)%>% 
  summarize(taxi_estimate=sum(estimate)) %>% 
  select(taxi_estimate)

survey_data<-survey_data %>% 
  filter(Q3_6 %in% c("Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips"))%>% 
  droplevels()
survey_data$Q3_6<-fct_expand(survey_data$Q3_6,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
survey_data$Q3_6<-fct_relevel(survey_data$Q3_6,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")

survey_data<-survey_data %>% 
  filter(Q3_7 %in% c("Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips"))%>% 
  droplevels()
survey_data$Q3_7<-fct_expand(survey_data$Q3_7,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
survey_data$Q3_7<-fct_relevel(survey_data$Q3_7,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")

survey_data<-survey_data %>% 
  filter(Q3_8 %in% c("Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips"))%>% 
  droplevels()
survey_data$Q3_8<-fct_expand(survey_data$Q3_8,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")
survey_data$Q3_8<-fct_relevel(survey_data$Q3_8,"Never", "Not every week" , "1-2 trips", "3-4 trips", "5-7 trips", "8-14 trips","15+ trips")




survey_data$Carshare_Type<-fct_relevel(survey_data$Carshare_Type,"Only Free-floating","Only Two-way","Two-way & Free-floating")


n<-tibble(Carshare_Type=c("Only Free-floating","Only Two-way","Two-way & Free-floating"))

  a<-survey_data %>%
  filter(!is.na(Carshare_Type)) %>% 
  group_by(Carshare_Type,Q3_1) %>% 
  summarize(count=n()) %>% 
  mutate(percentage=count/sum(count)) %>%
  mutate(v) %>% 
  mutate(estimate=percentage*v) %>% 
  summarize(walk_estimate=sum(estimate)) %>% 
  select(walk_estimate)


b<-survey_data %>%
  filter(!is.na(Carshare_Type)) %>% 
  group_by(Carshare_Type,Q3_2) %>% 
  summarize(count=n()) %>% 
  mutate(percentage=count/sum(count)) %>%
  mutate(v) %>% 
  mutate(estimate=percentage*v) %>% 
  summarize(bike_estimate=sum(estimate)) %>% 
  select(bike_estimate)


c<-survey_data %>%
  filter(!is.na(Carshare_Type)) %>%
  group_by(Carshare_Type,Q3_3) %>% 
  summarize(count=n()) %>% 
  mutate(percentage=count/sum(count)) %>%
  mutate(v) %>% 
  mutate(estimate=percentage*v) %>% 
  summarize(transit_estimate=sum(estimate)) %>% 
  select(transit_estimate)

d<-survey_data %>%
  filter(!is.na(Carshare_Type)) %>% 
  group_by(Carshare_Type,Q3_4) %>% 
  summarize(count=n()) %>% 
  mutate(percentage=count/sum(count)) %>%
  mutate(v) %>% 
  mutate(estimate=percentage*v) %>% 
  summarize(carpool_estimate=sum(estimate)) %>% 
  select(carpool_estimate)






  

f<-survey_data %>%
  filter(!is.na(Carshare_Type)) %>% 
  group_by(Carshare_Type,Q3_6) %>% 
  summarize(count=n()) %>% 
  mutate(percentage=count/sum(count)) %>%
  mutate(v) %>% 
  mutate(estimate=percentage*v) %>% 
  summarize(carshare_estimate=sum(estimate)) %>% 
  select(carshare_estimate)

g<-survey_data %>%
  filter(!is.na(Carshare_Type)) %>%
  group_by(Carshare_Type,Q3_7) %>% 
  summarize(count=n()) %>% 
  mutate(percentage=count/sum(count)) %>%
  mutate(v) %>% 
  mutate(estimate=percentage*v) %>% 
  summarize(car_passenger_estimate=sum(estimate)) %>% 
  select(car_passenger_estimate)

h<-survey_data %>%
  filter(!is.na(Carshare_Type)) %>% 
  group_by(Carshare_Type,Q3_8) %>% 
  summarize(count=n()) %>% 
  mutate(percentage=count/sum(count)) %>%
  mutate(v) %>% 
  mutate(estimate=percentage*v) %>% 
  summarize(car_driver_estimate=sum(estimate)) %>% 
  select(car_driver_estimate)


Carshare_Type_travel_estimates<-data.frame(n,a,b,c,d,e,f,g,h)
Carshare_Type_travel_estimates[,"Total"]<-rowSums(Carshare_Type_travel_estimates[,-(1)])

#Q30_travel_estimates
#write.csv(Q30_travel_estimates, "Q30_travel_estimates.csv",row.names = TRUE,col.names = TRUE)


Carshare_Type_travel_estimates_long<-gather(Carshare_Type_travel_estimates, mode, tripsPerWeek, walk_estimate:Total,factor_key=TRUE)

Carshare_Type_travel_estimates_together_chart<-Carshare_Type_travel_estimates_long %>% 
  ggplot(aes(y=Carshare_Type,x=tripsPerWeek))+
  geom_point(aes(color=Carshare_Type))+
  facet_wrap(~mode)+
  labs(y=str_wrap("What type of carsharing service(s) do you belong to?",width=40))+
  theme(legend.position = "none")


Carshare_Type_travel_estimates_long$mode<-fct_rev(fct_relevel(Carshare_Type_travel_estimates_long$mode,"walk_estimate", "bike_estimate","transit_estimate" ,"carshare_estimate",  "car_passenger_estimate" ,"carpool_estimate","car_driver_estimate","taxi_estimate" ))


Carshare_Type_best <-   Carshare_Type_travel_estimates_long %>%
  filter(mode!="Total") %>% 
  group_by(Carshare_Type) %>% 
  mutate(percent=100*(tripsPerWeek/sum(tripsPerWeek))) %>% 
  ggplot(aes(x=Carshare_Type,fill=mode))+
  geom_bar(aes(weight=percent),position = "stack")+
  theme_dark()+
  labs(y="Percentage of total trips per week",
       x="What type of carsharing service(s) do you belong to?")+
  theme(legend.title=element_blank(),
        plot.title = element_text(hjust = 0.5))+
  ggtitle("How many trips a week do you take?") +
  #scale_fill_manual(values=brewer.pal(n=8, "BuPu"))+
  geom_text(aes(y = percent, label = paste(round(percent,digits=1),"%",sep="")), position = position_stack(vjust = 0.5), size=3) +
  coord_flip()
Carshare_Type_best
```

```{r}
ggsave(filename = 'Two-WayVsFree-Floating/Q3TripEstimates_TypeOfCS_Percent.png', plot = Carshare_Type_best, device = 'png', width = 14, height = 6)
ggsave(filename = 'Two-WayVsFree-Floating/Q3TripEstimates_TypeOfCS_Aggregate.png', plot = Carshare_Type_travel_estimates_together_chart, device = 'png', width = 10, height = 6)
```


## affordability
```{r}
survey_data$Q30<-fct_relevel(survey_data$Q30,"Prefer not to answer" , "I/my household find living here unaffordable, or close to unaffordable", "I/my household meet our needs but cannot save for the future", "I/my household can comfortably meet our present and future needs")

CarshareType_Q30 <- survey_data %>%  
  filter(!is.na(Carshare_Type)) %>% 
  filter(!is.na(Q30)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Carshare_Type,Q30) %>%
  tally %>%
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Q30,y=percent, fill=Q30))+
  geom_bar(stat="identity")+
  facet_wrap(~Carshare_Type, ncol=1)+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none")+
  ggtitle("Affordability vs carsharing service") +
  labs(x="How affordable is your living situation",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  coord_flip()

 

CarshareType_Q30_alt <- survey_data %>%  
  filter(!is.na(Q30)) %>% 
  filter(!is.na(Carshare_Type)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Carshare_Type,Q30) %>%
  tally %>% 
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Carshare_Type,fill=Q30))+
  geom_bar(aes(weight=percent),position="stack")+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.title=element_blank())+
  ggtitle("Affordability vs carsharing service") +
  labs(x="What type of carsharing service(s) do you belong to",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  geom_text(aes(y = percent, label = paste(round(percent,digits=1),"%",sep="")), position = position_stack(vjust = 0.5), size=3)+
  coord_flip()

CarshareType_Q30
CarshareType_Q30_alt

```


```{r}
ggsave(filename = 'Two-WayVsFree-Floating/Q30Affordability_TypeOfCS.png', plot = CarshareType_Q30, device = 'png', width = 10, height = 10)
ggsave(filename = 'Two-WayVsFree-Floating/Q30Affordability_TypeOfCS_Alt.png', plot = CarshareType_Q30_alt, device = 'png', width = 10, height = 6)
```

## income
```{r}
survey_data$Q6<-fct_relevel(survey_data$Q6,"Less than one year"  , "1-2 years", "3-5 years", "6-10 years" , "11 years or longer")

survey_data$Q31<-fct_relevel(survey_data$Q31,"Over $150,000" , "$100,000 – $149,999" , "$75,000 – $99,999","$50,000 – $74,999", "$25,000 – $49,999", "Under $25,000")

CarshareType_Q31 <- survey_data %>%  
  filter(!is.na(Carshare_Type)) %>% 
  filter(!is.na(Q31)) %>%
  filter(!(Q9=="Yes"&Q31=="Find living here unaffordable")) %>% 
  group_by(Carshare_Type,Q31) %>%
  tally %>%
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Q31,y=percent, fill=Q31))+
  geom_bar(stat="identity")+
  facet_wrap(~Carshare_Type,ncol=1)+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none")+
  ggtitle("Income vs carsharing service(s)") +
  labs(x="Income",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=6, "RdYlGn")))+
  coord_flip()

 

CarshareType_Q31_alt <- survey_data %>%  
  filter(!is.na(Q31)) %>% 
  filter(!is.na(Carshare_Type)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Carshare_Type,Q31) %>%
  tally %>% 
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Carshare_Type,fill=Q31))+
  geom_bar(aes(weight=percent),position="stack")+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.title=element_blank())+
  ggtitle("Income vs carsharing service(s)") +
  labs(x="What type of cs service(s) do you belong to?",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=6, "RdYlGn")))+
  geom_text(aes(y = percent, label = paste(round(percent,digits=1),"%",sep="")), position = position_stack(vjust = 0.5), size=3)+
  coord_flip()

CarshareType_Q31
CarshareType_Q31_alt
```

```{r}
ggsave(filename = 'Two-WayVsFree-Floating/Q31Income_TypeOfCS.png', plot = CarshareType_Q31, device = 'png', width = 10, height = 8)
ggsave(filename = 'Two-WayVsFree-Floating/Q31Income_TypeOfCS_Alt.png', plot = CarshareType_Q31_alt, device = 'png', width = 10, height = 8)
```

## muni

```{r}

survey_data<-survey_data %>%
  filter(!is.na(Q2)) %>% 
  mutate(Muni = ifelse(Q2=="Vancouver", "Vancouver","Other B.C. Municipalities"))

survey_data$Q30<-fct_relevel(survey_data$Q30,"Prefer not to answer" , "I/my household find living here unaffordable, or close to unaffordable", "I/my household meet our needs but cannot save for the future", "I/my household can comfortably meet our present and future needs")

CarshareType_Muni <- survey_data %>%  
  filter(!is.na(Carshare_Type)) %>% 
  filter(!is.na(Muni)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Muni,Carshare_Type) %>%
  tally %>%
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Carshare_Type,y=percent, fill=Carshare_Type))+
  geom_bar(stat="identity")+
  facet_wrap(~Muni, ncol=1)+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none")+
  ggtitle("Municipality vs carsharing service") +
  labs(x="What type of carsharing service(s) do you belong to",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  coord_flip()

 

CarshareType_Muni_alt <- survey_data %>%  
  filter(!is.na(Muni)) %>% 
  filter(!is.na(Carshare_Type)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Muni, Carshare_Type) %>%
  tally %>% 
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Muni,fill=Carshare_Type))+
  geom_bar(aes(weight=percent),position="stack")+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.title=element_blank())+
  ggtitle("Municipality vs carsharing service") +
  labs(x="Municipality",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  geom_text(aes(y = percent, label = paste(round(percent,digits=1),"%",sep="")), position = position_stack(vjust = 0.5), size=3)+
  coord_flip()

CarshareType_Muni
CarshareType_Muni_alt

```

```{r}
ggsave(filename = 'Two-WayVsFree-Floating/Q2Muni_TypeOfCS.png', plot = CarshareType_Muni, device = 'png', width = 10, height = 8)
ggsave(filename = 'Two-WayVsFree-Floating/Q2Muni_TypeOfCS_Alt.png', plot = CarshareType_Muni_alt, device = 'png', width = 10, height = 8)
```



## age

```{r}

survey_data$Q30<-fct_relevel(survey_data$Q30,"Prefer not to answer" , "I/my household find living here unaffordable, or close to unaffordable", "I/my household meet our needs but cannot save for the future", "I/my household can comfortably meet our present and future needs")

CarshareType_Age <- survey_data %>%  
  filter(!is.na(Carshare_Type)) %>% 
  filter(!is.na(Q23)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Q23,Carshare_Type) %>%
  tally %>%
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Carshare_Type,y=percent, fill=Carshare_Type))+
  geom_bar(stat="identity")+
  facet_wrap(~Q23, ncol=1)+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none")+
  ggtitle("Age vs carsharing service") +
  labs(x="What type of carsharing service(s) do you belong to",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  coord_flip()

 

CarshareType_Age_alt <- survey_data %>%  
  filter(!is.na(Q23)) %>% 
  filter(!is.na(Carshare_Type)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Q23, Carshare_Type) %>%
  tally %>% 
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Q23,fill=Carshare_Type))+
  geom_bar(aes(weight=percent),position="stack")+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.title=element_blank())+
  ggtitle("Age vs carsharing service") +
  labs(x="Age",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  geom_text(aes(y = percent, label = paste(round(percent,digits=1),"%",sep="")), position = position_stack(vjust = 0.5), size=3)+
  coord_flip()

CarshareType_Age
CarshareType_Age_alt

```

```{r}
ggsave(filename = 'Two-WayVsFree-Floating/Q23Age_TypeOfCS.png', plot = CarshareType_Age, device = 'png', width = 10, height = 8)
ggsave(filename = 'Two-WayVsFree-Floating/Q23Age_TypeOfCS_Alt.png', plot = CarshareType_Age_alt, device = 'png', width = 10, height = 8)
```


## age flip

```{r}

survey_data$Q30<-fct_relevel(survey_data$Q30,"Prefer not to answer" , "I/my household find living here unaffordable, or close to unaffordable", "I/my household meet our needs but cannot save for the future", "I/my household can comfortably meet our present and future needs")

CarshareType_Age_Flip <- survey_data %>%  
  filter(!is.na(Carshare_Type)) %>% 
  filter(!is.na(Q23)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Carshare_Type,Q23) %>%
  tally %>%
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Q23,y=percent, fill=Q23))+
  geom_bar(stat="identity")+
  facet_wrap(~Carshare_Type, ncol=1)+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none")+
  ggtitle("Age vs carsharing service") +
  labs(x="Age",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=6, "RdYlGn")))+
  coord_flip()

 

CarshareType_Age_Flip_alt <- survey_data %>%  
  filter(!is.na(Q23)) %>% 
  filter(!is.na(Carshare_Type)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Carshare_Type,Q23) %>%
  tally %>% 
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Carshare_Type,fill=Q23))+
  geom_bar(aes(weight=percent),position="stack")+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.title=element_blank())+
  ggtitle("Age vs carsharing service") +
  labs(x="What type of carsharing service(s) do you belong to",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=6, "RdYlGn")))+
  geom_text(aes(y = percent, label = paste(round(percent,digits=1),"%",sep="")), position = position_stack(vjust = 0.5), size=3)+
  coord_flip()

CarshareType_Age_Flip
CarshareType_Age_Flip_alt

```

```{r}
ggsave(filename = 'Two-WayVsFree-Floating/Q23Age_TypeOfCS_Flip.png', plot = CarshareType_Age_Flip, device = 'png', width = 10, height = 8)
ggsave(filename = 'Two-WayVsFree-Floating/Q23Age_TypeOfCS_Alt_Flip.png', plot = CarshareType_Age_Flip_alt, device = 'png', width = 10, height = 8)
```


## length of carsharing

```{r}

survey_data$Q30<-fct_relevel(survey_data$Q30,"Prefer not to answer" , "I/my household find living here unaffordable, or close to unaffordable", "I/my household meet our needs but cannot save for the future", "I/my household can comfortably meet our present and future needs")

CarshareType_Length <- survey_data %>%  
  filter(!is.na(Carshare_Type)) %>% 
  filter(!is.na(Q6)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Q6,Carshare_Type) %>%
  tally %>%
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Carshare_Type,y=percent, fill=Carshare_Type))+
  geom_bar(stat="identity")+
  facet_wrap(~Q6, ncol=1)+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none")+
  ggtitle("Length of membership vs carsharing service") +
  labs(x="What type of carsharing service(s) do you belong to",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  coord_flip()

 

CarshareType_Length_alt <- survey_data %>%  
  filter(!is.na(Q6)) %>% 
  filter(!is.na(Carshare_Type)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Q6, Carshare_Type) %>%
  tally %>% 
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Q6,fill=Carshare_Type))+
  geom_bar(aes(weight=percent),position="stack")+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.title=element_blank())+
  ggtitle("Length of membership vs carsharing service") +
  labs(x="Length of membership",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  geom_text(aes(y = percent, label = paste(round(percent,digits=1),"%",sep="")), position = position_stack(vjust = 0.5), size=3)+
  coord_flip()

CarshareType_Length
CarshareType_Length_alt

```

```{r}
ggsave(filename = 'Two-WayVsFree-Floating/Q6Length_TypeOfCS.png', plot = CarshareType_Age, device = 'png', width = 10, height = 8)
ggsave(filename = 'Two-WayVsFree-Floating/Q6Length_TypeOfCS_Alt.png', plot = CarshareType_Age_alt, device = 'png', width = 10, height = 8)
```

## would you have acquired a vehicle?

```{r}

survey_data$Q30<-fct_relevel(survey_data$Q30,"Prefer not to answer" , "I/my household find living here unaffordable, or close to unaffordable", "I/my household meet our needs but cannot save for the future", "I/my household can comfortably meet our present and future needs")

CarshareType_Acquire <- survey_data %>%  
  filter(!is.na(Carshare_Type)) %>% 
  filter(!is.na(Q9)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Carshare_Type,Q9) %>%
  tally %>%
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Q9,y=percent, fill=Q9))+
  geom_bar(stat="identity")+
  facet_wrap(~Carshare_Type, ncol=1)+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none")+
  ggtitle("W/o cs, would you have acquired a vehicle vs carsharing service") +
  labs(x="W/o cs, would you have acquired a vehicle?",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  coord_flip()

 

CarshareType_Acquire_alt <- survey_data %>%  
  filter(!is.na(Q9)) %>% 
  filter(!is.na(Carshare_Type)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by( Carshare_Type,Q9) %>%
  tally %>% 
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Carshare_Type,fill=Q9))+
  geom_bar(aes(weight=percent),position="stack")+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("W/o cs, would you have acquired a vehicle vs carsharing service") +
  labs(x="What type of carsharing service(s) do you belong to",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  geom_text(aes(y = percent, label = paste(round(percent,digits=1),"%",sep="")), position = position_stack(vjust = 0.5), size=3)+
  labs(fill=str_wrap('W/o cs, would you have acquired a vehicle',width=15))+
  coord_flip()

CarshareType_Acquire
CarshareType_Acquire_alt

```

```{r}
ggsave(filename = 'Two-WayVsFree-Floating/Q9Acquire_TypeOfCS.png', plot = CarshareType_Acquire, device = 'png', width = 10, height = 8)
ggsave(filename = 'Two-WayVsFree-Floating/Q9Acquire_TypeOfCS_Alt.png', plot = CarshareType_Acquire_alt, device = 'png', width = 10, height = 8)
```


## Have you disposed of a vehicle??
```{r}

survey_data$Q30<-fct_relevel(survey_data$Q30,"Prefer not to answer" , "I/my household find living here unaffordable, or close to unaffordable", "I/my household meet our needs but cannot save for the future", "I/my household can comfortably meet our present and future needs")

CarshareType_Dispose <- survey_data %>%  
  filter(!is.na(Carshare_Type)) %>% 
  filter(!is.na(Q8)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Carshare_Type,Q8) %>%
  tally %>%
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Q8,y=percent, fill=Q8))+
  geom_bar(stat="identity")+
  facet_wrap(~Carshare_Type, ncol=1)+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none")+
  ggtitle("Have you disposed of a vehicle and used CS vs carsharing service") +
  labs(x="Have you disposed of a vehicle and used CS?",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  coord_flip()

 

CarshareType_Dispose_alt <- survey_data %>%  
  filter(!is.na(Q8)) %>% 
  filter(!is.na(Carshare_Type)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by( Carshare_Type,Q8) %>%
  tally %>% 
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Carshare_Type,fill=Q8))+
  geom_bar(aes(weight=percent),position="stack")+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("Have you disposed of a vehicle and used CS vs carsharing service") +
  labs(x="What type of carsharing service(s) do you belong to",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  geom_text(aes(y = percent, label = paste(round(percent,digits=1),"%",sep="")), position = position_stack(vjust = 0.5), size=3)+
  labs(fill=str_wrap('Have you disposed of a vehicle and used CS ',width=15))+
  coord_flip()

CarshareType_Dispose
CarshareType_Dispose_alt

```

```{r}
ggsave(filename = 'Two-WayVsFree-Floating/Q8Dispose_TypeOfCS.png', plot = CarshareType_Dispose, device = 'png', width = 10, height = 8)
ggsave(filename = 'Two-WayVsFree-Floating/Q8Dispose_TypeOfCS_Alt.png', plot = CarshareType_Dispose_alt, device = 'png', width = 10, height = 8)
```

## Have you disposed of anything?
```{r}

survey_data$Q30<-fct_relevel(survey_data$Q30,"Prefer not to answer" , "I/my household find living here unaffordable, or close to unaffordable", "I/my household meet our needs but cannot save for the future", "I/my household can comfortably meet our present and future needs")

CarshareType_Convenience <- survey_data %>%  
  filter(!is.na(Carshare_Type)) %>% 
  filter(!is.na(Q7_3)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by(Carshare_Type,Q7_3) %>%
  tally %>%
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Q7_3,y=percent, fill=Q7_3))+
  geom_bar(stat="identity")+
  facet_wrap(~Carshare_Type, ncol=1)+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none")+
  ggtitle("Do you use CS for convenience vs carsharing service") +
  labs(x="Do you use CS for convenience?",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  coord_flip()

 

CarshareType_Convenience_alt <- survey_data %>%  
  filter(!is.na(Q7_3)) %>% 
  filter(!is.na(Carshare_Type)) %>%
  filter(!(Q9=="Yes"&Q30=="Find living here unaffordable")) %>% 
  group_by( Carshare_Type,Q7_3) %>%
  tally %>% 
  mutate(percent=100*n/sum(n)) %>% 
  ggplot(aes(x=Carshare_Type,fill=Q7_3))+
  geom_bar(aes(weight=percent),position="stack")+
  theme_dark()+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("Do you use CS for convenience vs carsharing service") +
  labs(x="What type of carsharing service(s) do you belong to",
       y="Percent")+
  scale_fill_manual(values=rev(brewer.pal(n=5, "RdYlGn")))+
  geom_text(aes(y = percent, label = paste(round(percent,digits=1),"%",sep="")), position = position_stack(vjust = 0.5), size=3)+
  labs(fill=str_wrap('Do you use CS for convenience ',width=15))+
  coord_flip()

CarshareType_Convenience
CarshareType_Convenience_alt

```

```{r}
ggsave(filename = 'Two-WayVsFree-Floating/Q7_3Convenience_TypeOfCS.png', plot = CarshareType_Convenience, device = 'png', width = 10, height = 8)
ggsave(filename = 'Two-WayVsFree-Floating/Q7_3Convenience_TypeOfCS_Alt.png', plot = CarshareType_Convenience_alt, device = 'png', width = 14, height = 8)
```